---
title: "Pumilio_Turb_Final"
author: "Chloe Fouilloux"
date: '2023-02-01'
output: html_document
---

Welcome to our Oophaga pumilio tadpole turbidity code. You will find two other code files associated with this paper, (1) the Dendrobates tinctorius code, which involves a similar experiment with tadpoles from the Les Nouragues Field Station in French Guiana and (2) the water sample analysis file where I take spectrophotometry data and do color analysis of photographs.

In the following code, the values from (2) have already been calculated and are included in the data sheet. Please look at the "readme" file for variable descriptions.

First, let's load some packages

```{r pacakges}
library(dplyr)
library(ggplot2)
library(gghighlight)
library(ggtext)
library(gridExtra)
library(tidyverse)
library(forcats)
library(readr)
library(glmmTMB)
library(DHARMa)
library(lme4)
library(MASS)
library(sjPlot)
library(AICcmodavg)
library(corrplot)

```

Theme Set

```{r ggplot custom theme}
theme_set(  theme(legend.position = "right",
                  strip.background = element_rect(fill = "White"),
                  panel.background = element_rect(fill = "white",
                                                  colour = "black"), 
                  panel.grid.major = element_line(size = 0), 
                  panel.grid.minor = element_line(size = 0), 
                  text = element_text(size = 14)))
```

Now, let's load some data

```{r Data Wrangling}

las<- read_csv("LAS_VISION_FEB2023_3.csv")

las <- las %>%
       mutate(Trial = as.factor(Trial),
              Tad_ID = as.factor(Tad_ID),
              Condition = as.factor(Condition),
              Predator = as.factor(Predator)) 
#activity
activity <- las %>%
           filter (Condition != "Background") %>%
           dplyr::select(! c("White", "Black")) %>%
           mutate(mass_diff_cons = Mass - Cons_g, 
                  pr_z1 = Zone_1/60, 
                  pr_swim = Swim/60) %>%
        #normalizing RGB values to Rchannel, (x - xmin)/(xmax-xmin) --> xmin = 0, xmax = Rchannel
            mutate(rch_norm = rMean_OG/rMean_OG, 
                   gch_norm = gMean_OG/rMean_OG,
                   bch_norm = bMean_OG/rMean_OG)

activity$Predator<- forcats::fct_relevel(activity$Predator, 
                    c("Control", "Spider", "Conspecific"))

activity$Condition<- forcats::fct_relevel(activity$Condition, 
                    c("White", "Black"))

#Lets also look for black and white background trial
#background choice data
bw_choice_las <- las %>%
            filter (Condition == "Background") %>%
            mutate(p_black = Black/60, 
                   p_swim = Swim/60) 

```


################################### 

#### PCA

################################### 


So, here's the deal. Color is based in a RGB colour space, and it would be cool to be able to summarize these values into a single representative number. I thought that a PCA could be a cool way solve this issue, so let's give it a go!

```{r PCA for RGB colorspace.}
################
#Tidy Data PHOTOS----
###############
#PCA must be numeric so let's just subset the numeric variables.

numfrog <- las %>%
           dplyr::select(Tad_ID, rMean_OG, gMean_OG, bMean_OG)

#just numeric
random_frog<- las %>%
          dplyr::select(rMean_OG, gMean_OG, bMean_OG)

######## ######## ######## ########
# PCA MODEL PHOTOS ----
######## ######## ######## ########
#first we have to get all this data together
#remember our observation based PCA obs_PCA
dataset_obj = random_frog
obs_PCA = prcomp(dataset_obj,scale=T, center = T)
summary(obs_PCA)
axes <- predict(obs_PCA, newdata = random_frog) #
head(axes, 4)

PC_load<- as.data.frame(obs_PCA$rotation[,1:3]) #this is just loading for each variable, predict is better

dat <- cbind(numfrog, axes)

dat1<- dat %>%
      group_by(Tad_ID) %>%
      summarise(m_PC1 = max(PC1)) %>%
      mutate(Tad_ID = forcats::fct_reorder(Tad_ID, m_PC1))

dat2<- dplyr::full_join(activity, dat1, by = "Tad_ID") #nice

dat2$Condition<- forcats::fct_relevel(dat2$Condition, 
                    c("Black", "White"))


#NOW LET'S DO A PCA FOR THE SPECTROPHOTOMETER RGB VALUES! 

################
#Tidy Data SPECTROPHOTOMETER ----
###############
#PCA must be numeric so let's just subset the numeric variables.

numfrog1 <- las %>%
           dplyr::select(Tad_ID, R_spec, G_spec, B_Spec)

#just numeric
random_frog1<- las %>%
          dplyr::select(R_spec, G_spec, B_Spec)

######## ######## ######## ########
# PCA MODELS SPECTROPHOTOMETER----
######## ######## ######## ########
#first we have to get all this data together
#remember our observation based PCA obs_PCA
dataset_obj1 = random_frog1
obs_PCA1 = prcomp(dataset_obj1,scale=T, center = T)
summary(obs_PCA1)
axes1 <- predict(obs_PCA1, newdata = random_frog1) #
head(axes1, 4)

PC_load1<- as.data.frame(obs_PCA1$rotation[,1:3]) #this is just loading for each variable, predict is better

dat3 <- cbind(numfrog1, axes1)

dat4<- dat3 %>%
      group_by(Tad_ID) %>%
      summarise(m_PC1_spec = max(PC1)) %>%
      mutate(Tad_ID = forcats::fct_reorder(Tad_ID, m_PC1_spec))

#joining the photodata with the spectrophotometer data
dat4.1<- dplyr::full_join(dat1, dat4, by = "Tad_ID")

#joining the two pca components to the full data sheet
dat2<- dplyr::full_join(activity, dat4.1, by = "Tad_ID") #nice

dat2$Condition<- forcats::fct_relevel(dat2$Condition, 
                    c("Black", "White"))

#relationship between spectrophotometry and photography RGB values
#monotonic increase
ggplot(dat2, aes(y= m_PC1, x= m_PC1_spec, fill = m_PC1_spec))+
  geom_point(size = 3, shape = 21) + 
  xlab("PC1 component from spectrophotometer RGB values") +
  ylab("PC1 component from photography RGB values")+
  stat_smooth(method = "gam", 
              formula = y ~ poly(x, 2), 
              colour = "black") + 
  stat_smooth(method = "gam", 
              geom = "ribbon", 
              linetype = "dashed",
              formula = y ~ poly(x,2), 
              colour = "black", 
              fill = NA) +
  scale_fill_gradient(high = "white", low = "#5c1f27") +
  theme(legend.position = "None")


#Correlation between two PC components

dat4.1_num <- dat4.1 %>%
              dplyr::select(m_PC1, m_PC1_spec)

#here alternative hypothesis is greater, as I would assume a positive relationship between the two variables.
cor.test(dat4.1_num$m_PC1, dat4.1_num$m_PC1_spec, 
         alternative = "greater", method = "pearson")

#broadening the relationship to include monotonic dynamic here might is a good option
cor.test(dat4.1_num$m_PC1, dat4.1_num$m_PC1_spec, 
        method = "spearman", exact = F)


## Adding to dat2 for plotting purposes

dat2 <- dat2 %>%
        mutate(dark_light = ifelse(m_PC1 <= 0.5, "Turbid microhabitat", "Clear microhabitat"))

mean_pred <- dat2 %>%
            group_by(Condition, dark_light, Predator)%>%
            summarise(mean_swim = mean(pr_swim), 
                      med_swim = median(pr_swim)) %>%
            drop_na()

```

################################### 

#### Statistics

################################### 


** Now, for *O. pumilio* data we also have photograph data that we can compare with spectrophotometer data. Let's run the exact same model formulation with using photography and spectrophotometry data. **

Below we will be looking at models parameterized with (1) mean maximum transmittance values from full spectra measured from spectrophotometer and (2) also the PC1 (from PCA above) for photos of the same pools. If these models have the same output, then this provides us with more evidence to support the fact that these two measures provide very similar quantifications of pool turbidity! :-) 

# Space use (Zone 1)

```{r Zone 1 counts by tadpoles with Transmittance or PC1}

### Let's start with the tranmsmittance data ###

#full model
z1_trans<- glmmTMB(Zone_1 ~ Condition * Predator * (Mean_Trans) + 
                (Mass)+
               (1|Tad_ID), 
              data = activity, family = nbinom1) 

summary(z1_trans) #3 way interactoin 0.052
simulationOutput <- simulateResiduals(fittedModel = z1_trans)
plot(simulationOutput)

#Check three way interaction removed let's play around with the interactions

#Condition * Predator
z1_trans1<- glmmTMB(Zone_1 ~ Condition * Predator + (Mean_Trans) + 
                (Mass)+
               (1|Tad_ID), 
              data = activity, family = nbinom1) 
summary(z1_trans1)

#Predator * (Mean_Trans)
z1_trans2<- glmmTMB(Zone_1 ~ Condition + Predator * (Mean_Trans) + 
                (Mass)+
               (1|Tad_ID), 
              data = activity, family = nbinom1) 

#Condition* (Mean_Trans)
z1_trans3<- glmmTMB(Zone_1 ~ Condition  * (Mean_Trans) + Predator +
                (Mass)+
               (1|Tad_ID), 
              data = activity, family = nbinom1) 


#Condition + Predator
z1_trans4<- glmmTMB(Zone_1 ~ Condition + Predator + (Mean_Trans) + 
                (Mass)+
               (1|Tad_ID), 
              data = activity, family = nbinom1) 



#Let's compare model fits via AICc
aic.cand<- list(z1_trans1, z1_trans2, z1_trans3, z1_trans4)
mods<- c("z1_trans1", "z1_trans2", "z1_trans3", "z1_trans4")
aictab(aic.cand, mods, sort = T, second.ord = T)

#additive model wins
#interaction ns in z1_trans3
summary(z1_trans4)

####################
#what about with PC1
####################

z1_pc1<- glmmTMB(Zone_1 ~ Condition * Predator * m_PC1 + 
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 

#Condition * Predator 
z1_pc1_2<- glmmTMB(Zone_1 ~ Condition * Predator + m_PC1 + 
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 


#Predator * m_PC1
z1_pc1_3<- glmmTMB(Zone_1 ~ Condition + Predator * m_PC1 + 
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 

#Predator * m_PC1
z1_pc1_4<- glmmTMB(Zone_1 ~ Condition  * (m_PC1) + Predator +
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 


z1_pc1_5<- glmmTMB(Zone_1 ~ Condition + Predator + m_PC1 + 
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 

summary(z1_pc1_5) 

#Let's compare model fits via AICc
aic.cand<- list(z1_pc1_2, z1_pc1_3, z1_pc1_4, z1_pc1_5)
mods<- c("z1_pc1_2", "z1_pc1_3", "z1_pc1_4", "z1_pc1_5")
aictab(aic.cand, mods, sort = T, second.ord = T)

#additive model wins, same as spectrophotometer data!!! 
summary(z1_pc1_5)

```


```{r Zone 1 DHARMA Checks}

#Let's check the model fit and residuals using DHARMa
summary(z1_pc1_4)
summary(z1_trans4)

#run both lines at the same time
simulationOutput <- simulateResiduals(fittedModel = z1_pc1_5) #no problems detected
plot(simulationOutput)
#
testDispersion(z1_pc1_4) #fine
testZeroInflation(z1_pc1_4) #good

#tab model for photography data
tab_model(z1_pc1_5, 
          transform = NULL,
          show.ci = F, 
          show.est = T, 
          show.se = T, 
          show.stat = T,
          show.obs = F,
          show.r2 = F,
          string.stat = "z value",
          string.se = "SE", 
          dv.labels = "<i>O. pumilio</i> space use (zone 1 counts)",
          pred.labels = c("(Intercept)",
                         "Condition [White]",
                        "Predator [Spider]",
                         "Predator [Cons.]", 
                         "PC1",
                         "Mass"))


```

(2) Alright, there are two main ways to think about the tadpole size in this study. The first is to think about the absolute size of the focal tadpole (in grams) and the other is to think about the weight difference between the tadpole and the visual stimuli when faced with conspecifics. Here, I show that the model output does not change as a fuction of using one variable or the other. Ultimately, the size of the focal tadpole seems to be the most important predictive factor rather than relative size between tadpoles.


What about using Transmittance and our PC1 component?
Transmittance is just a conversion of absoption T = (1-Abs)


# ACTIVITY (SWIMMING)

Great! Now let's move on to activity!


As with the previous formulation, we will start with a full model interaction

```{r Swimming Activity Models }

op_swim_m1_full<- glmmTMB(Swim ~ 
                Condition * Predator * (Mean_Trans) + 
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 

summary(op_swim_m1_full) 

#Check three way interaction removed
step(op_swim_m1_full)

####
# Trying different interaction structures#
####

#Condition * Predator
m3a<- glmmTMB(Swim ~ 
                Condition * Predator + Mean_Trans + 
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 


#Predator * Mean_Wave
m3b<- glmmTMB(Swim ~ 
                Condition + Predator * Mean_Trans + 
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 

#Condition * Mean_Wave
m3c<- glmmTMB(Swim ~ 
                Condition * Mean_Trans +  Predator +
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 

#Additive model
m3d<- glmmTMB(Swim ~ 
                Condition + Mean_Trans +  Predator +
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 


#Let's compare model fits via AICc
aic.cand<- list(m3a, m3b, m3c, m3d)
mods<- c("m3a", "m3b", "m3c", "m3d")
aictab(aic.cand, mods, sort = T, second.ord = T)

#m3c, by a lot!

##### ##### 
## PC1 ##
#######  ##### 

op_swim_m1_pho<- glmmTMB(Swim ~ 
                Condition * Predator * m_PC1 + 
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 

summary(op_swim_m1_pho) 

#Check three way interaction removed
step(op_swim_m1_pho)

####
# Trying different interaction structures#
####

#Condition * Predator
m3a_pc1<- glmmTMB(Swim ~ 
                Condition * Predator + m_PC1 + 
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 


#Predator * PC1
m3b_pc1<- glmmTMB(Swim ~ 
                Condition + Predator * m_PC1 + 
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 

#Condition * m_PC1
m3c_pc1<- glmmTMB(Swim ~ 
                Condition * m_PC1+  Predator +
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 

#Additive model
m3d_pc1<- glmmTMB(Swim ~ 
                Condition + Predator +  m_PC1 +
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 


#Let's compare model fits via AICc
aic.cand<- list(m3a_pc1, m3b_pc1, m3c_pc1, m3d_pc1)
mods<- c("m3a_pc1", "m3b_pc1", "m3c_pc1", "m3d_pc1")
aictab(aic.cand, mods, sort = T, second.ord = T)

summary(m3c_pc1)

#tab model for photography data
tab_model(m3c_pc1, 
          transform = NULL,
          show.ci = F, 
          show.est = T, 
          show.se = T, 
          show.stat = T,
          show.obs = F,
          show.r2 = F,
          string.stat = "z value",
          string.se = "SE", 
          dv.labels = "<i>O. pumilio</i> activity (swim counts)",
          pred.labels = c("(Intercept)",
                         "Condition [White]",
                         "PC1", 
                         "Predator [Spider]",
                         "Predator [Cons.]", 
                         "Mass", 
                         "Condition [White]: PC1"))


```

Now let's check the quality of m3c

```{r Swimming Checks DHARMA}

#Let's check the model fit and residuals using DHARMa
summary(m3c_pc1)

#run both lines at the same time
simulationOutput <- simulateResiduals(fittedModel = m3c_pc1) #no problems detected
plot(simulationOutput)
#
testDispersion(m3c_pc1) #fine
testZeroInflation(m3c_pc1) #good


#For fun, let's reshuffle the levels so we have white as the intercept and rerun the model. Remember, as a base our model intercept is "black, control". If we relevel our model than we can have everything compared to the "white, control".
levels(dat2$Condition)

dat2$Condition<- forcats::fct_relevel(dat2$Condition, 
                    c( "White", "Black"))

#Condition * m_PC1
m3c_pc1<- glmmTMB(Swim ~ 
                Condition * m_PC1+  Predator +
                (Mass)+
               (1|Tad_ID), 
              data = dat2, family = nbinom1) 

summary(m3c_pc1)

```


```{r Comapring Model Outputs}

##################################### ######### ######### 
##### Mean Max. Trans vesus PC1 for Zone1 + Swim #####
############################ ######### ######### ######### 
#Let's check the model fit and residuals using DHARMa
summary(z1_pc1_5) #zone 1 using PC1
summary(z1_trans4) #zone 1 using transmission data 

#Let's compare model fits via AICc
aic.cand<- list(z1_pc1_5, z1_trans4)
mods<- c("z1_pc1_5", "z1_trans4")
aictab(aic.cand, mods, sort = T, second.ord = T)

#Let's check the model fit and residuals using DHARMa
summary(m3c) #swim using trans
summary(m3c_pc1) #swim using pc1

#Let's compare model fits via AICc
aic.cand<- list(m3c, m3c_pc1)
mods<- c("m3c", "m3c_pc1")
aictab(aic.cand, mods, sort = T, second.ord = T)

############################
##### Absolute vs. Relative Tadpole Size #####
############################ 

#best model for zone 1 was z1_trans4, ADDITIVE MODEL

summary(z1_trans4)

#let's run this with mass difference data for ZONE1
z1_trans4.md <- glmmTMB(Zone_1 ~ 
                Condition + Mean_Trans + Predator + 
                mass_diff_cons+ (1|Tad_ID), 
                data = dat2, family = nbinom1) 

summary(z1_trans4.md)
simulationOutput <- simulateResiduals(fittedModel = z1_trans4.md)
plot(simulationOutput)

#Let's compare model fits via AICc
aic.cand<- list(z1_trans4, z1_trans4.md)
mods<- c("z1_trans4", "z1_trans4.md")
aictab(aic.cand, mods, sort = T, second.ord = T)

#######################################################

summary(m3c)

#let's run this with mass difference data for SWIM
m3c.md <- glmmTMB(Swim ~ 
                Condition * Mean_Trans + Predator + 
                mass_diff_cons+ (1|Tad_ID), 
              data = dat2, family = nbinom1) 

summary(m3c.md)
simulationOutput <- simulateResiduals(fittedModel = m3c.md)
plot(simulationOutput)

#Let's compare model fits via AICc
aic.cand<- list(m3c, m3c.md)
mods<- c("m3c", "m3c.md")
aictab(aic.cand, mods, sort = T, second.ord = T)

```

Well that sure was fun. In the code above we were able to show that models with mass difference between tadpoles or focal tadpole mass yielded the same results as did models parameterized with either photography or spectrophotometry data. Cool beans!


Now let's get some plotting fun, huh?

#Black and White background choice
```{r PLOTTING: B + W Choice}

#White/black preference ####

#With mean wave
ggplot(bw_choice_las, aes(x = Mass, y = p_black))+
  annotate(geom = "rect", 
           fill = "black",
           color = "black",
           alpha = 0.5,
           xmin = -Inf,
           xmax = Inf,
           ymin = 0.5,
           ymax = Inf)+
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "white") + 
  geom_point(size = 3, shape = 21, stroke = 1.5, 
             aes(fill = Mean_Wave)) +  #rMean_OG
  ylab("Prp. spent on black background")+
  xlab("Tadpole mass (g)") + 
  scale_fill_gradient(low = "white", high = "#5c1f27", 
  name = "Mean absorbance coefficient") 

```

#Zone 1 choice

```{r Zone 1 with Spectral Data}

## ** favourite ** ##

## MEAN WAVELENGTH AND POOL CHOICE FACET BY PREDATOR
z1_pum<-ggplot(activity, aes( y = pr_z1, x = Predator, colour = Predator)) + 
annotate(geom = "rect", 
             xmin = -Inf, xmax = 1.5, 
             ymin = -Inf, ymax = Inf, 
             fill = "lightgreen", 
             alpha = 0.2)+
geom_jitter(size = 3,stroke = 1, alpha = 0.3, 
            height = 0, width = 0.08) +
  geom_rect( data = data.frame(Condition = "Black"),
            aes(ymin = 0.35, ymax = 0.55, xmin = -Inf, xmax = Inf), 
            inherit.aes = F, fill = "lightgrey", colour = "black", 
            alpha = 0.4, linetype = "dashed", size = 0.2) + 
 geom_rect( data = data.frame(Condition = "White"),
            aes(ymin = 0.15, ymax = 0.35, xmin = -Inf, xmax = Inf), 
            inherit.aes = F, fill = "lightgrey", colour = "black", 
            alpha = 0.4, linetype = "dashed", size = 0.2) + 
facet_wrap(~ Condition)+
  stat_summary(fun.data = mean_cl_boot, #lets look at mean instead of median
                 geom = "pointrange", # could also do crossbar, errorbar
                 shape = 21,
                 stroke = 1.5,
                 color = "black",
                 fill = "white",
                 size = 0.8) +
ylab("Proportion spent in zone 1") +
xlab("Visual stimulus")+
scale_color_brewer(palette = "Accent")+
coord_cartesian(ylim = c(0,1)) + 
theme(legend.position = "None")

ggsave("z1_pum.png", plot = z1_pum, width = 18, height = 11, units = "cm")


##### Weak 3 way interaction from model op_zone1_m1_full #####

ggplot(dat2, aes(y = pr_z1, x = m_PC1 , color = Predator)) + #Mean_wave  
geom_point(size = 2, shape = 21, stroke = 1)+
    facet_wrap(~ Condition + Predator) +
    stat_smooth(method = "gam", 
                formula = y ~ s(x, bs = "cs"), 
                aes(fill = Predator), 
                alpha = 0.2)+ #y ~ s(x, bs = "cs"), log(x)
    ylab("Proportion spent in Zone 1") +
    xlab("PC1") + 
    scale_color_brewer(palette = "Accent") +
    scale_fill_brewer(palette = "Accent") +
    coord_cartesian(ylim = c(0,1)) + 
  theme(legend.position = "None")

```

#Swimming

```{r PLOTTING: SWIM AND SPECTRAL}

#Swimming activity FACETED BY CONDITION
pum_swim<-
ggplot(dat2, aes( y = pr_swim, x = m_PC1)) + #Mean_Wave
geom_point(size = 3, shape = 21, stroke = 1, 
           aes(fill = m_PC1), alpha = 0.7) + #Mean_Wave
    facet_wrap(~ Condition) +
       stat_smooth(method = "gam", 
               formula = y ~ (x), #log(x) 
               color = "black", 
               size = 1, 
               fullrange = T)+
  ylab("Proportion of time spent swimming") +
   xlab("PC1") + 
  #expression(Nursery~mean~wavelength~Delta * tilde(nu)/cm^-1)
 scale_fill_gradient(high = "white", low = "#5c1f27", 
                    name = "PC1") +
  #expression(Delta * tilde(nu)/cm^-1)
geom_richtext(data = data.frame(Condition = "White"),
     aes(x = 2, y =0.25), color = "black", 
     label = "Light nursery tadpoles swim<br>**more** in white conditions", size = 3)+
#geom_richtext(data = data.frame(Condition = "White"),
     #aes(x = 20, y = 0.03), color = "black", 
     #label = "Dark nursery tadpoles swim<br>**less** in white conditions", size = 3)+
coord_cartesian(ylim = c(0, 1))+
scale_color_brewer(palette = "Accent") + 
theme(legend.text = element_text(size = 10), 
        legend.title = element_text(size = 10)) + 
  labs(tag = "A")

pum_swim


#Swimming activity FACETED BY CONDITION
pum_mass<- 
ggplot(activity, aes( y = pr_swim , x = Mass)) +
geom_point(size = 3, shape = 21, stroke = 1, alpha = 0.6, 
           fill = "lightblue") +
       stat_smooth(method = "glm", 
               formula = y ~ (x), 
               color = "black", 
               size = 1)+
         stat_smooth(method = "gam", 
               geom = "ribbon",
               linetype = "dashed",
               colour = "black",
               fill = NA,
               formula = y ~ x)+
    ylab("Proportion of time spent swimming") +
   xlab("Focal tadpole mass (g)") +
   labs(tag = "B") + 
  coord_cartesian(ylim = c(0,1))

pum_mass


```

# TEST for species comparison plot

```{r Swim Test}
#for pum it's PC1 * background
#for tinc its PC1 * pred

#subset(activity, !is.na(dark_light)

#with medians for cutoff at m_PC1 = 0.5
swim_pum<-
  ggplot(dat2) +
geom_jitter(size = 3,stroke = 1, alpha = 0.3, 
            height = 0, width = 0.08,
             aes(y = pr_swim, x = Predator, colour = Predator)) +
  facet_wrap(~ dark_light) +
    geom_point(data = data.frame(dark_light = "Turbid microhabitat"),
             y = 0.083333333, x = 1, shape = 21,
             fill = "white", size = 3.4, colour= "grey", stroke = 1.5)+
  geom_point(data = data.frame(dark_light = "Turbid microhabitat"),
             y = 0.033333333, x = 2, shape = 21,
             fill = "white", size = 3.4, colour= "grey", stroke = 1.5)+
   geom_point(data = data.frame(dark_light = "Turbid microhabitat"),
             y = 0.066666667, x = 3, shape = 21,
             fill = "white", size = 3.4, colour= "grey", stroke = 1.5)+
    geom_point(data = data.frame(dark_light = "Turbid microhabitat"),
             y = 0.100000000, x = 1, shape = 21,
             fill = "black", size = 3.4, colour= "grey", stroke = 1.5)+
  geom_point(data = data.frame(dark_light = "Turbid microhabitat"),
             y = 0.083333333, x = 2, shape = 21,
             fill = "black", size = 3.4, colour= "grey", stroke = 1.5)+
   geom_point(data = data.frame(dark_light = "Turbid microhabitat"),
             y = 0.100000000, x = 3, shape = 21,
             fill = "black", size = 3.4, colour= "grey", stroke = 1.5)+
  #clear
   geom_point(data = data.frame(dark_light = "Clear microhabitat"),
             y = 0.008333333, x = 1, shape = 21,
             fill = "black", size = 3.4, colour= "grey", stroke = 1.5)+
  geom_point(data = data.frame(dark_light = "Clear microhabitat"),
             y = 0.000000000, x = 2, shape = 21,
             fill = "black", size = 3.4, colour= "grey", stroke = 1.5)+
   geom_point(data = data.frame(dark_light = "Clear microhabitat"),
             y = 0.041666667, x = 3, shape = 21,
             fill = "black", size = 3.4, colour= "grey", stroke = 1.5)+
    geom_point(data = data.frame(dark_light = "Clear microhabitat"),
             y = 0.091666667, x = 1, shape = 21,
             fill = "white", size = 3.4, colour= "grey", stroke = 1.5)+
  geom_point(data = data.frame(dark_light = "Clear microhabitat"),
             y = 0.075000000, x = 2, shape = 21,
             fill = "white", size = 3.4, colour= "grey", stroke = 1.5)+
   geom_point(data = data.frame(dark_light = "Clear microhabitat"),
             y = 0.075000000, x = 3, shape = 21,
             fill = "white", size = 3.4, colour= "grey", stroke = 1.5)+
  
  ylab("Proportion spent swimming") +
  xlab("Visual stimulus") + 
  #scale_fill_gradient(high = "white", low = "#5c1f27", 
                     # name = "Reflectance") +
  scale_color_brewer(palette = "Accent") + 
  coord_cartesian(ylim = c(0, 1)) + 
  guides(colour = "none")

ggsave("swim_pum.png", plot = swim_pum, width = 18, height = 11, units = "cm")

```


### PHOTOGRAPHY AND COLOUR ###
Alright, as you know we also have these photos that were taken the day that the water samples were collected.


```{r Photography and R channel}

#using mean max transmittance and PCA 1 components
ggplot(dat2, aes(x = Mean_Trans, y = m_PC1)) + #Mean absorbance across three technical replicates
  geom_point(aes(fill = Mean_Trans), shape = 21, size = 3) + 
  stat_smooth(method = "gam", 
              formula = y ~ (x), 
              color = "black", 
              fullrange = T) +
   # stat_smooth(method = "gam", 
             # formula = y ~ log(x), 
             # color = "black", 
              #fullrange = F) +
    #stat_smooth(method = "gam", 
              #formula = y ~ (x), 
             # color = "blue") +
   scale_fill_gradient(high = "white", low = "#5c1f27", 
                    name = "Mean maximum full-spectra transmittance (T)") +
  xlab("Mean max. transmittance")+
  ylab("Principal component 1 (RGB)") + 
  ylim(-2.5, 2.5)+
  theme(legend.position = "None")

```
