---
title: "Tinctorius Turbidity Final "
author: "Chloe Fouilloux"
date: '2023-02-01'
output: html_document
---

Welcome to our Dendrobates tinctorius tadpole turbidity code. You will find two other code files associated with this paper, (1) the Oophaga pumilio code, which involves a similar experiment with tadpoles from the La Selva Field Station in Costa Rica and (2) the water sample analysis file where I take spectrophotometry data and do color analysis of photographs. 

In the following code, the values from (2) have already been calculated and are included in the data sheet. Please look at the "readme" file for variable descriptions.



First, let's load some packages

```{r}

#Let's see what we're working with here. 
library(ggplot2)
library(dplyr)
library(tidyverse)
library(RColorBrewer)
library(gridExtra)
library(forcats)
library(ggtext)
library(glmmTMB)
library(ggforce)
library(lme4)
library(DHARMa)
library(AICcmodavg)
library(sjPlot)

```

First, I like to set a global theme for my data vis. at the beginning of the script, so let's do that now. 

```{r}
#Theme Set----
theme_set(  theme(legend.position = "right",
                  strip.background = element_rect(fill = "White"),
                  panel.background = element_rect(fill = "white",
                                                  colour = "black"), 
                  panel.grid.major = element_line(size = 0), 
                  panel.grid.minor = element_line(size = 0), 
                  text = element_text(size = 14)))

```


Let's read in our turbidity data from Les Nouragues, French Guiana 2022

```{r}
turb<- read.csv("FG_TURB_JAN2023.csv", sep=",")

#Now let's tidy our data and create some new variables 

turb<- turb %>%
       mutate(Pred = replace_na(Predator, "None"))
#Activity Zone 1, 2, 3 data

activity <- turb %>%
           filter (Condition != "Background") %>%
           dplyr::select(! c("White", "Black")) %>%
           mutate(p_swim = Swim/60, 
                  p_rest = Rest/60,
                  p_zone1 = Zone_1/60,
                  mass_diff_cons = Mass - Cons_g, 
                  mass_diff_pred = Mass - Odon_g, 
                  Predator = as.factor(Predator), 
                  Pool_ID = as.factor(Pool_ID),
                  Condition = as.factor(Condition), 
                  Pool_Type = as.factor(Pool_Type), 
                  Predator_Y_N = as.factor(Predator_Y_N)) %>%
          mutate(Pred_0_1 = ifelse(Predator_Y_N == "Y", 1, 0)) %>%
          mutate(dark_light = ifelse(rMean_OG <= 100, "Turbid microhabitat", "Clear microhabitat")) %>%
          mutate(
         pool_vol_ellipcyl = (pi)*(0.5*Length)*(0.5*Width)*Depth, 
    #pi*(0.5Length)*(0.5Width)*Depth = elliptic cylinder,
    #https://mathmonks.com/cylinder/volume-of-a-cylinder 
        pool_vol_semiellipse = ((4/3)*(pi)*(0.5*Length)*(0.5*Width)*Depth)/2,
    #bibi paper, semi ellipse
        pool_dens_cyl = Tad_Density_Cons/pool_vol_ellipcyl, 
        pool_dens_semiell = Tad_Density_Cons/pool_vol_semiellipse)

#calculating pool volume, and thus, conspecific density

mean_pred <- activity %>%
            group_by(Predator, dark_light)%>%
            summarise(mean_swim = mean(p_swim), 
                      med_swim = median(p_swim)) %>%
            drop_na()

#background choice data
bw_choice <- turb %>%
            filter (Condition == "Background") %>%
            mutate(p_black = Black/60, 
                   p_swim = Swim/60, 
                   Pool_ID = as.factor(Pool_ID))
            

activity$Pool_ID<- forcats::fct_relevel(activity$Pool_ID, c("22-12", "22-14", "22-4", 
                                        "22-22.1", "22-9","22-27", "22-8",
                                         "22-22.2", "22-43",
                                        "22-18"))

levels(activity$Pool_ID)
```



###################################
#### Statistics ####
###################################

# Space use (Zone 1)

```{r Zone 1 counts by tadpoles}

dt_zone1_m1_full<- glmmTMB(Zone_1 ~ 
               Condition * Predator *log(rMean_OG) + 
               Tad_Density_Cons +  
               Predator_Y_N + 
               Mass+
               #offset((Mass)) +
               (1|Pool_ID) + (1|TadID), 
             data = activity, family = nbinom1) 

summary(dt_zone1_m1_full)
#Remove three way interaction
step(dt_zone1_m1_full)


####
# Trying different interaction structures#
####

#Condition * Predator
m2a<- glmmTMB(Zone_1 ~ 
                Condition * Predator +log(rMean_OG) + 
                Tad_Density_Cons +  
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = activity, family = nbinom1) 

#Predator * log(rMean_OG) 
m2b<- glmmTMB(Zone_1 ~ 
               Condition + Predator * log(rMean_OG) + 
               Tad_Density_Cons +  
               Predator_Y_N + 
               Mass+
               (1|Pool_ID) + (1|TadID), 
             data = activity, family = nbinom1) 

#Condition * log(rMean_OG)
m2c<- glmmTMB(Zone_1 ~ 
                Condition * log(rMean_OG) + Predator +
                Tad_Density_Cons +  
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = activity, family = nbinom1)

#dropping all interactions
m2d<- glmmTMB(Zone_1 ~ 
                Condition + log(rMean_OG) + Predator +
                Tad_Density_Cons +  
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = activity, family = nbinom1) 


#Let's compare model fits via AICc
aic.cand<- list(m2a, m2b, m2c, m2d)
mods<- c("m2a", "m2b", "m2c", "m2d")
aictab(aic.cand, mods, sort = T, second.ord = T)

```

What do we see from the models above? Well, none of the interactions are significant, no matter how we spin them around. When we compare all of the models via AICc, the additive model fits best. So, there ya have it! <3

```{r Zone 1 Checks and Table}

#Let's check the model fit and residuals using DHARMa
summary(m2d)

#run both lines at the same time
simulationOutput <- simulateResiduals(fittedModel = m2d) #no problems detected
plot(simulationOutput)
#
testDispersion(m2d) #fine
testZeroInflation(m2d) #good


#now let's put this output into a single table
tab_model(m2d, 
          transform = NULL,
          show.ci = F, 
          show.est = T, 
          show.se = T, 
          show.stat = T,
          show.obs = F,
          show.r2 = F,
          string.stat = "z value",
          string.se = "SE", 
          dv.labels = "<i>D. tinctorius</i> Space-use (zone 1 counts)",
          pred.labels = c("(Intercept)",
                          "Condition [White]",
                          "Predator [Conspecific]", 
                          "log(% R-ch reflectance)", 
                          "Wild consp. density",
                          "Wild predator presence (Y/N)",
                          "Mass"))

```

Great! Now let's move on to activity!

# Activity (swimming)

As with the previous formulation, we will start with a full model interaction

```{r Swimming Activity Models}

dt_swim_m1_full <-glmmTMB(Swim ~ 
                Condition * Predator *log(rMean_OG) + 
                Tad_Density_Cons + 
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = activity, family = nbinom1) 

summary(dt_swim_m1_full) #p= 0.07 for a 3-way interaction

step(dt_swim_m1_full)
#Lets try dropping the insig. 3 way interaction


####
# Trying different interaction structures#
####

#Predator * log(rMean_OG), significant interaction
m3a<- glmmTMB(Swim ~ 
               Condition + Predator * log(rMean_OG) + 
               Tad_Density_Cons + 
               Predator_Y_N + 
               Mass+
               (1|Pool_ID) + (1|TadID), 
             data = activity, family = nbinom1) 

#Condition * Predator
m3b<- glmmTMB(Swim ~ 
                Condition * Predator + log(rMean_OG) + 
                Tad_Density_Cons +  
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = activity, family = nbinom1) 

#Condition *log(rMean_OG)
m3c<- glmmTMB(Swim ~ 
                Condition *log(rMean_OG) +  Predator + 
                Tad_Density_Cons +
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = activity, family = nbinom1) 

#dropping all interactions
m3d<- glmmTMB(Swim ~ 
                Condition +log(rMean_OG) +  Predator + 
                Tad_Density_Cons + 
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = activity, family = nbinom1) 

#Let's compare model fits via AICc
aic.cand<- list(m3a, m3b, m3c, m3d)
mods<- c("m3a", "m3b", "m3c", "m3d")
aictab(aic.cand, mods, sort = T, second.ord = T)

#model 3a

```

From the models above, we find that model 3a, which has an interaction between nursery turbidity and visual stimulus is the best fit. 
Let's go and plot and check it. 

```{r Swimming Check and Table}


#Let's check the model fit and residuals using DHARMa
summary(m3a)

#run both lines at the same time
simulationOutput <- simulateResiduals(fittedModel = m3a) #no problems detected
plot(simulationOutput)
#
testDispersion(m3a) #fine
testZeroInflation(m3a) #good


#now let's put this output into a single table

tab_model(m3a, 
          transform = NULL,
          show.ci = F, 
          show.est = T, 
          show.se = T, 
          show.stat = T,
          show.obs = F,
          show.r2 = F,
          string.stat = "z value",
          string.se = "SE", 
          dv.labels = "<i>D. tinctorius</i> Activity (swim counts)",
          pred.labels = c("(Intercept)",
                          "Condition [White]",
                          "Predator [Conspecific]", 
                          "log(% R ch. reflectance)", 
                          "Wild consp. count",
                          "Wild predator presence (Y/N)",
                          "Mass",
                          "Predator [Conspecific] * log(% R ch. reflectance)"))


```


###################################
#### Absolute vs. Relative Tadpole Size ####
###################################

Alright, there are two main ways to think about the tadpole size in this study. The first is to think about the absolute size of the focal tadpole (in grams) and the other is to think about the weight difference between the tadpole and the visual stimuli when faced with conspecifics. Here, I show that the model output does not change as a fuction of using one variable or the other. Ultimately, the size of the focal tadpole seems to be the most important predictive factor rather than relative size between tadpoles. 

```{r Absolute vs. Relative Size Model Checks}
# models for ** zone use **
# here both models are suitable, good DHARMa, mass difference or absolute mass not significant in either
# AIC within less than 2 between either model

# 1. m2d,  Condition + Predator +log(rMean_OG) + Tad_Density_Cons +  Predator_Y_N + Mass+ (1|Pool_ID) + (1|TadID)
# 2. m2d.md, 
m2d.md<- glmmTMB(Zone_1 ~ 
                   Condition + Predator +log(rMean_OG) + 
                   Tad_Density_Cons +  
                   Predator_Y_N + 
                   mass_diff_cons+
                   (1|Pool_ID) + (1|TadID), 
                 data = activity, family = nbinom1) 
summary(m2d)
simulationOutput <- simulateResiduals(fittedModel = m2d.md)
plot(simulationOutput)

AIC(m2d, m2d.md)

# models for ** swimming **
# here both models are suitable, good DHARMa, mass difference or absolute mass not significant in either
# AIC within less than 2 between either model

#1. m3a, Condition + Predator * log(rMean_OG) + Tad_Density_Cons + Predator_Y_N + Mass+ (1|Pool_ID) + (1|TadID)
#2. m3a.md 
m3a.md<- glmmTMB(Swim ~ 
                  Condition + Predator * log(rMean_OG) + 
                  Tad_Density_Cons +  #this can be removed!
                  Predator_Y_N + 
                  mass_diff_cons+
                  (1|Pool_ID) + (1|TadID), 
                 data = activity, family = nbinom1)
summary(m3a.md)
simulationOutput <- simulateResiduals(fittedModel = m3a.md)
plot(simulationOutput)

AIC(m3a, m3a.md)

```




###################################
#### Plotting ####
###################################



Yeehaw, my favourite part! Now let's get some sexy graphs up on there :-) 

#Black and White Background Choice
```{r Black + White Choice Plot}

ggplot(bw_choice, aes(x = Mass, y = p_black, fill = rMean_OG))+ #x = Swim
  annotate(geom = "rect", 
           fill = "black",
           color = "black",
           alpha = 0.5,
           xmin = -Inf,
           xmax = Inf,
           ymin = 0.5,
           ymax = Inf)+
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "white") + 
  geom_point(size = 3, shape = 21, stroke = 1.5) + 
  ylab("Prp. spent on black background")+
  xlab("Tadpole mass (g)") +
  scale_fill_gradient(high = "white", low = "#5c1f27", 
  name = "% R-channel reflectance") 


```


#Time spent in Zone 1

```{r Zone 1 Plots}

#Zone 1 choice background + predator
ggplot(activity, aes( y = p_zone1, x = Predator, colour = Predator)) + 
 #no control here
   #annotate(geom = "rect", 
          # xmin = -Inf, xmax = 1.5, 
          # ymin = -Inf, ymax = Inf, 
          # fill = "lightgreen", 
           #alpha = 0.2)+
  geom_jitter(size = 3,stroke = 1, alpha = 0.3, 
              height = 0, width = 0.08) +
  geom_rect( data = data.frame(Condition = "Black"),
             aes(ymin = 0.05, ymax = 0.21, xmin = -Inf, xmax = Inf), 
             inherit.aes = F, fill = "lightgrey", colour = "black", 
             alpha = 0.4, linetype = "dashed", size = 0.2) + 
  geom_rect( data = data.frame(Condition = "White"),
             aes(ymin = 0.12, ymax = 0.28, xmin = -Inf, xmax = Inf), 
             inherit.aes = F, fill = "lightgrey", colour = "black", 
             alpha = 0.4, linetype = "dashed", size = 0.2) + 
  facet_wrap(~ Condition)+
  stat_summary(fun.data = mean_cl_boot, #lets look at mean instead of median
               geom = "pointrange", # could also do crossbar, errorbar
               shape = 21,
               stroke = 1.5,
               color = "black",
               fill = "white",
               size = 0.8) +
  ylab("Proportion spent in zone 1") +
  scale_color_manual(values = c("#386CB0", "#FDC086"))+
  #scale_color_brewer(palette = "Accent")+
  coord_cartesian(ylim = c(0,1)) + 
  theme(legend.position = "None")


#Zone 1 based on nursery conspecific density
 ggplot(activity, aes( y = p_zone1, x = pool_dens_semiell)) +   #Tad_Density_Cons
  geom_point(size = 3, shape = 21, fill = "lightblue") +
  #facet_wrap(~ Predator)+
  ylab("Proportion spent in Zone 1") +
  stat_smooth( #aes(colour = Predator), 
    method = "gam", 
    geom = "ribbon",
    linetype = "dashed",
    formula = y ~ (x), #y ~ s(x, bs = "cs"), log(x)
    fill = NA, 
    colour = "black")+
  stat_smooth( #aes(colour = Predator), 
               method = "gam", 
               formula = y ~ (x), #y ~ s(x, bs = "cs"), log(x)
               fill = "grey", 
               colour = "black")+
  xlab("Wild nursery conspecific count") + 
  #scale_color_brewer(palette = "Accent")+
  coord_cartesian(ylim = c(0,1)) 
  
```


#Swimming

```{r Swimming Plots}

ggplot(subset(activity, !is.na(dark_light))) +
  geom_point(size = 3, shape = 21, stroke = 0.5, 
             aes(y = p_swim, x = Predator, fill = rMean_OG), alpha = 0.7) +
  geom_segment(data = data.frame(dark_light = "Clear microhabitat"),
               aes(x = 1, xend = 2, y = 0.07500000, yend = 0.19166667),
               linetype = "dashed", colour = "grey", inherit.aes = F)+
  geom_segment(data = data.frame(dark_light = "Turbid microhabitat"),
               aes(x = 1, xend = 2, y = 0.01666667, yend = 0),
               linetype = "dashed", colour = "grey", inherit.aes = F)+
  facet_wrap(~ dark_light) +
  geom_point(data = mean_pred, aes(y = med_swim, x = Predator), shape = 21,
             fill = "red", size = 3.4, colour= "black", stroke = 1.5)+
 # geom_point(data = mean_pred, aes(y = med_swim, x = Predator), 
             #colour = "red", size = 5, shape = 21)+
  ylab("Proportion of time spent swimming") +
  xlab("Predator") + 
  scale_fill_gradient(high = "white", low = "#5c1f27", 
                      name = "Reflectance") +
  coord_cartesian(ylim = c(0, 1)) + 
  guides(fill = "none")


```


#Ecological Information

```{r Conspecifics in microhabitats}

#conspecific count
ggplot(subset(bw_choice, !(Predator_Y_N == "NA")),
       aes(x = Predator_Y_N, y = Tad_Density_Cons))+  #y = Swim
  geom_jitter(size = 3, shape = 21, stroke = 1.5, alpha = 0.6,
              height = 0, width = 0.1, aes(fill = Pool_Type)) +
  stat_summary(fun.data = mean_cl_boot, #lets look at mean instead of median
               geom = "pointrange", # could also do crossbar, errorbar
               shape = 21,
               color = "black",
               fill = "white",
               size = 1, 
               stroke = 1.4) + 
  scale_fill_brewer(palette = "Spectral", 
                    name = "Pool type") + 
  xlab("Heterospecific Nursery predator (Y/N)") + 
  ylab("Nursery conspecific count") +
  geom_richtext(aes(x = 0.8, y =10), color = "black", 
                label = "*D. tinctorius*", size = 4)

#how about for actual density calculation
ggplot(subset(bw_choice, !(Predator_Y_N == "NA")),
       aes(x = Predator_Y_N, y = pool_dens_semiell, colour = Pool_Type))+  #y = pool_dens_cyl
  geom_jitter(size = 3, shape = 21, stroke = 1.5, alpha = 0.6,
              height = 0, width = 0.1) +
  stat_summary(fun.data = mean_cl_boot, #lets look at mean instead of median
               geom = "pointrange", # could also do crossbar, errorbar
               shape = 21,
               color = "black",
               fill = "white",
               size = 1, 
               stroke = 1.4) + 
  scale_fill_brewer(palette = "Spectral", 
                    name = "Pool type") + 
  xlab("Heterospecific Nursery predator (Y/N)") + 
  ylab("Nursery conspecific density") 


#not more predators in darker pools
ggplot(subset(bw_choice, !(Predator_Y_N == "NA")), 
              aes(x = Predator_Y_N, y = rMean_OG))+  #y = Swim
  geom_jitter(size = 3, shape = 21, stroke = 1.5, alpha = 0.6,
              height = 0.2, width = 0.1, aes(fill = Pool_Type)) +
  stat_summary(fun.data = mean_cl_boot, #lets look at mean instead of median
               geom = "pointrange", # could also do crossbar, errorbar
               shape = 21,
               color = "black",
               fill = "white",
               size = 1, 
               stroke = 1.4) + 
  scale_fill_brewer(palette = "Spectral", 
                    name = "Pool Type") + 
  xlab("Nursery predator (Y/N)") + 
  ylab("%R-channel reflectance")

```
























