---
title: "Tinctorius Turbidity Final "
author: "Chloe Fouilloux"
date: '2023-02-01'
output: html_document
---

Welcome to our Dendrobates tinctorius tadpole turbidity code. You will find two other code files associated with this paper, (1) the Oophaga pumilio code, which involves a similar experiment with tadpoles from the La Selva Field Station in Costa Rica and (2) the water sample analysis file where I take spectrophotometry data and do color analysis of photographs.

In the following code, the values from (2) have already been calculated and are included in the data sheet. Please look at the "readme" file for variable descriptions.

First, let's load some packages

```{r Packages}

#Let's see what we're working with here. 
library(ggplot2)
library(dplyr)
library(tidyverse)
library(RColorBrewer)
library(gghighlight)
library(gridExtra)
library(forcats)
library(ggtext)
library(glmmTMB)
library(ggforce)
library(lme4)
library(DHARMa)
library(AICcmodavg)
library(sjPlot)

```

First, I like to set a global theme for my data vis. at the beginning of the script, so let's do that now.

```{r Theme Set for ggplot2}
#Theme Set----
theme_set(  theme(legend.position = "right",
                  strip.background = element_rect(fill = "White"),
                  panel.background = element_rect(fill = "white",
                                                  colour = "black"), 
                  panel.grid.major = element_line(size = 0), 
                  panel.grid.minor = element_line(size = 0), 
                  text = element_text(size = 14)))

```

Let's read in our turbidity data from Les Nouragues, French Guiana 2022

```{r Data wrangling}
turb<- read.csv("FG_TURB_JAN2023.csv", sep=",")

#Now let's tidy our data and create some new variables 

turb<- turb %>%
       mutate(Pred = replace_na(Predator, "None"))
#Activity Zone 1, 2, 3 data

activity <- turb %>%
           filter (Condition != "Background") %>%
           dplyr::select(! c("White", "Black")) %>%
           mutate(p_swim = Swim/60, 
                  p_rest = Rest/60,
                  p_zone1 = Zone_1/60,
                  mass_diff_cons = Mass - Cons_g, 
                  mass_diff_pred = Mass - Odon_g, 
                  Predator = as.factor(Predator), 
                  Pool_ID = as.factor(Pool_ID),
                  Condition = as.factor(Condition), 
                  Pool_Type = as.factor(Pool_Type), 
                  Predator_Y_N = as.factor(Predator_Y_N)) %>%
          mutate(Pred_0_1 = ifelse(Predator_Y_N == "Y", 1, 0)) %>%
          mutate(dark_light = ifelse(rMean_OG <= 100, "Turbid microhabitat", "Clear microhabitat")) %>%
          mutate(
         pool_vol_ellipcyl = (pi)*(0.5*Length)*(0.5*Width)*Depth, 
    #pi*(0.5Length)*(0.5Width)*Depth = elliptic cylinder,
    #https://mathmonks.com/cylinder/volume-of-a-cylinder 
        pool_vol_semiellipse = ((4/3)*(pi)*(0.5*Length)*(0.5*Width)*Depth)/2,
    #bibi paper, semi ellipse
        pool_dens_cyl = Tad_Density_Cons/pool_vol_ellipcyl, 
        pool_dens_semiell = Tad_Density_Cons/pool_vol_semiellipse)

#calculating pool volume, and thus, conspecific density

#background choice data
bw_choice <- turb %>%
            filter (Condition == "Background") %>%
            mutate(p_black = Black/60, 
                   p_swim = Swim/60, 
                   Pool_ID = as.factor(Pool_ID))
            

activity$Pool_ID<- forcats::fct_relevel(activity$Pool_ID, c("22-12", "22-14", "22-4", 
                                        "22-22.1", "22-9","22-27", "22-8",
                                         "22-22.2", "22-43",
                                        "22-18"))

levels(activity$Pool_ID)
```


################################### 

#### PCA   

################################### 

So, here's the deal. Color is based in a RGB colour space, and it would be cool to be able to summarize these values into a single representative number. I thought that a PCA could be a cool way solve this issue, so let's give it a go!

As we show in the pumilio script, where both photos and spectrophotometer were available, the principle component from the RGB space yielded the same model results as the transmission data! So that's pretty neat. Having this helps validate the photos ~ spectrophotometer relationship.

In the pumilio data, we see that more positive PC1 numbers represent less turbid pools, while more negative numbers represent darker/more turbid pools. Let's see what happens here (spoiler alert: same trend. check the supplements of the paper for the cool graphs that ground-truth this!)

```{r PCA for RGB colorspace for tincs}
################
#Tidy Data----
###############
#PCA must be numeric so let's just subset the numeric variables.

numfrog <- activity %>%
           dplyr::select(Pool_ID, rMean_OG, gMean_OG, bMean_OG)%>%
          tidyr::drop_na()

#just numeric
random_frog<- activity %>%
          dplyr::select(rMean_OG, gMean_OG, bMean_OG) %>%
          tidyr::drop_na()

######## ######## ######## ########
# PCA MODELS ----
######## ######## ######## ########
#first we have to get all this data together
#remember our observation based PCA obs_PCA
dataset_obj = random_frog
obs_PCA = prcomp(dataset_obj,scale=T, center = T)
summary(obs_PCA)
axes <- predict(obs_PCA, newdata = random_frog) #
head(axes, 4)

PC_load<- as.data.frame(obs_PCA$rotation[,1:3])
#this is just loading for each variable, predict is better

dat <- cbind(numfrog, axes)

dat1<- dat %>%
      group_by(Pool_ID) %>%
      summarise(m_PC1 = max(PC1)) %>%
      mutate(Pool_ID = forcats::fct_reorder(Pool_ID, m_PC1))

dat2<- dplyr::full_join(activity, dat1, by = "Pool_ID") #nice

ggplot(dat1, aes(x = Pool_ID, y = m_PC1))+
  geom_point(size = 3) + 
  xlab("Pool ID") + 
  ylab("PC1") +
  theme( axis.text.y = element_text(size = 20), 
         axis.title.y = element_text(size = 20))

#Playing around with Dat2 for data viz
dat2 <- dat2 %>%
        mutate(dark_light = ifelse(m_PC1 <= 0, "Turbid microhabitat", "Clear microhabitat"))

mean_pred <- dat2 %>%
            group_by(Condition, dark_light, Predator)%>%
            summarise(mean_swim = mean(p_swim), 
                      med_swim = median(p_swim)) %>%
            drop_na()

```

################################### 

#### Statistics with PCA

################################### 

# Space use (Zone 1)

Here the relationship between PC1 and max. transmittance is linear, not logged so we do not need to log the relationship.

```{r PCA:: Zone 1 counts by tadpoles}

dt_zone1_m1_full<- glmmTMB(
              Zone_1 ~ 
               Condition * Predator *(m_PC1) + 
               Tad_Density_Cons +  
               Predator_Y_N + 
               Mass+
               #offset((Mass)) +
               (1|Pool_ID) + (1|TadID), 
             data = dat2, family = nbinom1) 

summary(dt_zone1_m1_full) #tad density + condition white
#Remove three way interaction
step(dt_zone1_m1_full)


####
# Trying different interaction structures#
####

dat2$Predator<- forcats::fct_relevel(dat2$Predator, 
                    c( "Odonata", "Conspecific"))
levels(dat2$Predator)

#Condition * Predator
m2a<- glmmTMB(Zone_1 ~ 
                Condition * Predator + (m_PC1) + 
                Tad_Density_Cons +  
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = dat2, family = nbinom1) 


#Predator * (m_PC1)
m2b<- glmmTMB(Zone_1 ~ 
                Condition + Predator * (m_PC1) + 
                Tad_Density_Cons +  
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = dat2, family = nbinom1) 


#Condition  * (m_PC1)
m2c<- glmmTMB(Zone_1 ~ 
                Condition  * (m_PC1) + Predator +
                Tad_Density_Cons +  
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = dat2, family = nbinom1) 

#none of the above interactions significant

#additive model
m2d<- glmmTMB(Zone_1 ~ 
                Condition  + (m_PC1) + Predator +
                Tad_Density_Cons +  
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = dat2, family = nbinom1) 


summary(m2d)

#Let's compare model fits via AICc
aic.cand<- list(m2a, m2b, m2c, m2d)
mods<- c("m2a", "m2b", "m2c", "m2d")
aictab(aic.cand, mods, sort = T, second.ord = T) #Great, model m2d!
```

What do we see from the models above? Well, none of the interactions are significant, no matter how we spin them around. When we compare all of the models via AICc, the additive model fits best. So, there ya have it! \<3

```{r PCA1:: Zone 1 Checks and Table}

#Let's check the model fit and residuals using DHARMa
summary(m2d)

#run both lines at the same time
simulationOutput <- simulateResiduals(fittedModel = m2d) #no problems detected
plot(simulationOutput)
#
testDispersion(m2d) #fine
testZeroInflation(m2d) #good


#now let's put this output into a single table
tab_model(m2d, 
          transform = NULL,
          show.ci = F, 
          show.est = T, 
          show.se = T, 
          show.stat = T,
          show.obs = F,
          show.r2 = F,
          string.stat = "z value",
          string.se = "SE", 
          dv.labels = "<i>D. tinctorius</i> space use (zone 1 counts)",
          pred.labels = c("(Intercept)",
                          "Condition [White]",
                          "PC1", 
                          "Predator [Conspecific]", 
                          "Wild consp. count",
                          "Wild predator presence (Y/N)",
                          "Mass"))

```

Great! Now let's move on to activity!

# Activity (swimming)
As with the previous formulation, we will start with a full model interaction


```{r PCA:: Swimming Activity Models}

dt_swim_m1_full <-glmmTMB(
                Swim ~ 
                Condition * Predator * m_PC1 + 
                Tad_Density_Cons + 
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = dat2, family = nbinom1) 

#run both lines at the same time
simulationOutput <- simulateResiduals(fittedModel = m3a) #no problems detected
plot(simulationOutput)
#
testDispersion(m3a) #fine
testZeroInflation(m3a) #good

summary(dt_swim_m1_full) #p= 0.022 for a 3-way interaction, but model seems overfit

step(dt_swim_m1_full)

####
# Trying different interaction structures#
####

#Predator * log(rMean_OG), significant interaction
m3a<- glmmTMB(Swim ~ 
               Condition + Predator * m_PC1 + 
               Tad_Density_Cons + 
               Predator_Y_N + 
               Mass+
               (1|Pool_ID) + (1|TadID), 
             data = dat2, family = nbinom1) 

#Condition * Predator
m3b<- glmmTMB(Swim ~ 
                Condition * Predator + m_PC1 + 
                Tad_Density_Cons +  
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = dat2, family = nbinom1) 

#Condition * m_PC1
m3c<- glmmTMB(Swim ~ 
                Condition *m_PC1 +  Predator + 
                Tad_Density_Cons +
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = dat2, family = nbinom1) 

#dropping all interactions
m3d<- glmmTMB(Swim ~ 
                Condition + m_PC1 +  Predator + 
                Tad_Density_Cons + 
                Predator_Y_N + 
                Mass+
                (1|Pool_ID) + (1|TadID), 
              data = dat2, family = nbinom1) 

#Let's compare model fits via AICc
aic.cand<- list(m3a, m3b, m3c, m3d)
mods<- c("m3a", "m3b", "m3c", "m3d")
aictab(aic.cand, mods, sort = T, second.ord = T)

#model 3a, b, d are all within 2AICc
summary(m3a)
#model 3a: sig. cons*PC1 interaction
#model 3b: no sig. interaction, sig cons + PC1
#model 3d:additive model, sig PC1 + background

#Keep significant interaction and lowest AICc

#run both lines at the same time
simulationOutput <- simulateResiduals(fittedModel = m3a) #no problems detected
plot(simulationOutput)
#
testDispersion(m3a) #fine
testZeroInflation(m3a) #good

```


From the models above, we find that model 3a, which has an interaction between nursery turbidity and visual stimulus is the best fit. Let's go and plot and check it.

```{r Swimming Check and Table}

#Let's check the model fit and residuals using DHARMa
summary(m3a)

#run both lines at the same time
simulationOutput <- simulateResiduals(fittedModel = m3a) #no problems detected
plot(simulationOutput)
#
testDispersion(m3a) #fine
testZeroInflation(m3a) #good


#now let's put this output into a single table

tab_model(m3a, 
          transform = NULL,
          show.ci = F, 
          show.est = T, 
          show.se = T, 
          show.stat = T,
          show.obs = F,
          show.r2 = F,
          string.stat = "z value",
          string.se = "SE", 
          dv.labels = "<i>D. tinctorius</i> activity (swim counts)",
          pred.labels = c("(Intercept)",
                          "Condition [White]",
                          "Predator [Conspecific]", 
                          "PC1", 
                          "Wild consp. count",
                          "Wild predator presence (Y/N)",
                          "Mass",
                          "Predator [Conspecific] * PC1"))


```

################################### 

#### Absolute vs. Relative Tadpole Size

################################### 

Alright, there are two main ways to think about the tadpole size in this study. The first is to think about the absolute size of the focal tadpole (in grams) and the other is to think about the weight difference between the tadpole and the visual stimuli when faced with conspecifics. Here, I show that the model output does not change as a fuction of using one variable or the other. Ultimately, the size of the focal tadpole seems to be the most important predictive factor rather than relative size between tadpoles.

```{r Absolute vs. Relative Size Model Checks}
# models for ** zone use **
# here both models are suitable, good DHARMa, mass difference or absolute mass not significant in either
# AIC within less than 2 between either model

# 1. m2d,  Condition + Predator + PC1 + Tad_Density_Cons +  Predator_Y_N + Mass+ (1|Pool_ID) + (1|TadID)
# 2. m2d.md, 
m2d.md<- glmmTMB(Zone_1 ~ 
                   Condition + Predator + m_PC1 + 
                   Tad_Density_Cons +  
                   Predator_Y_N + 
                   mass_diff_cons+
                   (1|Pool_ID) + (1|TadID), 
                 data = dat2, family = nbinom1) 

simulationOutput <- simulateResiduals(fittedModel = m2d.md)
plot(simulationOutput)

#Let's compare model fits via AICc
aic.cand<- list(m2d, m2d.md)
mods<- c("m2d", "m2d.md")
aictab(aic.cand, mods, sort = T, second.ord = T)
# models for ** swimming **
# here both models are suitable, good DHARMa, mass difference or absolute mass not significant in either
# AIC within less than 2 between either model

#1. m3a, Condition + Predator * PC1 + Tad_Density_Cons + Predator_Y_N + Mass+ (1|Pool_ID) + (1|TadID)
#2. m3a.md 
m3a.md<- glmmTMB(Swim ~ 
                  Condition + Predator * m_PC1 + 
                  Tad_Density_Cons +  
                  Predator_Y_N + 
                  mass_diff_cons+
                  (1|Pool_ID) + (1|TadID), 
                 data = dat2, family = nbinom1)
summary(m3a.md)
simulationOutput <- simulateResiduals(fittedModel = m3a.md)
plot(simulationOutput)

#Let's compare model fits via AICc
aic.cand<- list(m3a, m3a.md)
mods<- c("m3d", "m3d.md")
aictab(aic.cand, mods, sort = T, second.ord = T)

```

################################### 

#### Plotting

################################### 

Yeehaw, my favourite part! Now let's get some sexy graphs up on there :-)

#Black and White Background Choice

```{r Black + White Choice Plot}

ggplot(bw_choice, aes(x = Mass, y = p_black, fill = rMean_OG))+ #x = Swim
  annotate(geom = "rect", 
           fill = "black",
           color = "black",
           alpha = 0.5,
           xmin = -Inf,
           xmax = Inf,
           ymin = 0.5,
           ymax = Inf)+
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "white") + 
  geom_point(size = 3, shape = 21, stroke = 1.5) + 
  ylab("Prp. spent on black background")+
  xlab("Tadpole mass (g)") +
  scale_fill_gradient(high = "white", low = "#5c1f27", 
  name = "% R-channel reflectance") 

```

#Time spent in Zone 1

```{r Zone 1 Plots}


dat2$Predator<- forcats::fct_relevel(dat2$Predator, 
                    c("Odonata", "Conspecific"))

#Zone 1 choice background + predator

z1_plot<-
ggplot(dat2, aes( y = p_zone1, x = Predator, colour = Predator)) + 
 #no control here
   #annotate(geom = "rect", 
          # xmin = -Inf, xmax = 1.5, 
          # ymin = -Inf, ymax = Inf, 
          # fill = "lightgreen", 
           #alpha = 0.2)+
  geom_jitter(size = 3,stroke = 1, alpha = 0.3, 
              height = 0, width = 0.08) +
  #geom_rect( data = data.frame(Condition = "Black"),
            # aes(ymin = 0.05, ymax = 0.21, xmin = -Inf, xmax = Inf), 
            # inherit.aes = F, fill = "lightgrey", colour = "black", 
            # alpha = 0.4, linetype = "dashed", size = 0.2) + 
 # geom_rect( data = data.frame(Condition = "White"),
           #  aes(ymin = 0.12, ymax = 0.28, xmin = -Inf, xmax = Inf), 
            # inherit.aes = F, fill = "lightgrey", colour = "black", 
            # alpha = 0.4, linetype = "dashed", size = 0.2) + 
  facet_wrap(~ Condition)+
  stat_summary(fun.data = mean_cl_boot, #lets look at mean instead of median
               geom = "pointrange", # could also do crossbar, errorbar
               shape = 21,
               stroke = 1.5,
               color = "black",
               fill = "white",
               size = 0.8) +
  ylab("Proportion spent in zone 1") +
  xlab("Visual stimulus")+
  scale_color_manual(values = c("#386CB0", "#FDC086"))+
  #scale_color_brewer(palette = "Accent")+
  coord_cartesian(ylim = c(0,1)) + 
  theme(legend.position = "None")

z1_plot

ggsave("z1_plot.png", plot = z1_plot, width = 18, height = 11, units = "cm")

#Zone 1 based on nursery conspecific density
 ggplot(activity, aes( y = p_zone1, x = pool_dens_semiell)) +   #Tad_Density_Cons
  geom_point(size = 3, shape = 21, fill = "lightblue") +
  #facet_wrap(~ Predator)+
  ylab("Proportion spent in Zone 1") +
  stat_smooth( #aes(colour = Predator), 
    method = "gam", 
    geom = "ribbon",
    linetype = "dashed",
    formula = y ~ (x), #y ~ s(x, bs = "cs"), log(x)
    fill = NA, 
    colour = "black")+
  stat_smooth( #aes(colour = Predator), 
               method = "gam", 
               formula = y ~ (x), #y ~ s(x, bs = "cs"), log(x)
               fill = "grey", 
               colour = "black")+
  xlab("Wild nursery conspecific count") + 
  #scale_color_brewer(palette = "Accent")+
  coord_cartesian(ylim = c(0,1)) 
  
```

#Swimming

```{r Swimming Plots}

ggplot(subset(activity, !is.na(dark_light))) +
  geom_point(size = 3,stroke = 0.5, 
             aes(y = p_swim, x = Predator, colour = Predator), alpha = 0.7) +
  geom_segment(data = data.frame(dark_light = "Clear microhabitat"),
               aes(x = 1, xend = 2, y = 0.07500000, yend = 0.19166667),
               linetype = "dashed", colour = "grey", inherit.aes = F)+
  geom_segment(data = data.frame(dark_light = "Turbid microhabitat"),
               aes(x = 1, xend = 2, y = 0.01666667, yend = 0),
               linetype = "dashed", colour = "grey", inherit.aes = F)+
  facet_wrap(~ dark_light) +
  geom_point(data = mean_pred, aes(y = med_swim, x = Predator), shape = 21,
             fill = "red", size = 3.4, colour= "black", stroke = 1.5)+
 # geom_point(data = mean_pred, aes(y = med_swim, x = Predator), 
             #colour = "red", size = 5, shape = 21)+
  ylab("Proportion of time spent swimming") +
  xlab("Visual stimulus") + 
  scale_color_manual(values = c("#386CB0", "#FDC086"))+
  coord_cartesian(ylim = c(0, 1)) + 
  guides(fill = "none")

#tinc swim

swim_tinc<-
  ggplot(subset(dat2, !is.na(dark_light))) +
  geom_jitter(size = 3,stroke = 1, alpha = 0.3, 
            height = 0, width = 0.08, 
            aes(y = p_swim, x = Predator, colour = Predator), alpha = 0.7) +
  facet_wrap(~ dark_light) +
    geom_point(data = data.frame(dark_light = "Turbid microhabitat"),
             y = 0.03333333, x = 1, shape = 21,
             fill = "white", size = 3.4, colour= "grey", stroke = 1.5)+
  geom_point(data = data.frame(dark_light = "Turbid microhabitat"),
             y = 0.00000000, x = 2, shape = 21,
             fill = "white", size = 3.4, colour= "grey", stroke = 1.5)+
    geom_point(data = data.frame(dark_light = "Turbid microhabitat"),
             y = 0.00000000, x = 1, shape = 21,
             fill = "black", size = 3.4, colour= "grey", stroke = 1.5)+
  geom_point(data = data.frame(dark_light = "Turbid microhabitat"),
             y = 0.00000000, x = 2, shape = 21,
             fill = "black", size = 3.4, colour= "grey", stroke = 1.5)+
  #clear
   geom_point(data = data.frame(dark_light = "Clear microhabitat"),
             y = 0.06666667, x = 1, shape = 21,
             fill = "black", size = 3.4, colour= "grey", stroke = 1.5)+
  geom_point(data = data.frame(dark_light = "Clear microhabitat"),
             y = 0.17500000, x = 2, shape = 21,
             fill = "black", size = 3.4, colour= "grey", stroke = 1.5)+
    geom_point(data = data.frame(dark_light = "Clear microhabitat"),
             y = 0.15000000, x = 1, shape = 21,
             fill = "white", size = 3.4, colour= "grey", stroke = 1.5)+
  geom_point(data = data.frame(dark_light = "Clear microhabitat"),
             y = 0.20000000, x = 2, shape = 21,
             fill = "white", size = 3.4, colour= "grey", stroke = 1.5)+
  ylab("Proportion spent swimming") +
  xlab("Visual stimulus") + 
 scale_color_manual(values = c("#386CB0", "#FDC086"))+
  coord_cartesian(ylim = c(0, 1)) + 
  guides(colour = "none")

ggsave("swim_tinc.png", plot = swim_tinc, width = 18, height = 11, units = "cm")


```

#Ecological Information

```{r Conspecifics in microhabitats}

#conspecific count
ggplot(subset(bw_choice, !(Predator_Y_N == "NA")),
       aes(x = Predator_Y_N, y = Tad_Density_Cons))+  #y = Swim
  geom_jitter(size = 3, shape = 21, stroke = 1.5, alpha = 0.6,
              height = 0, width = 0.1, aes(fill = Pool_Type)) +
  stat_summary(fun.data = mean_cl_boot, #lets look at mean instead of median
               geom = "pointrange", # could also do crossbar, errorbar
               shape = 21,
               color = "black",
               fill = "white",
               size = 1, 
               stroke = 1.4) + 
  scale_fill_brewer(palette = "Spectral", 
                    name = "Pool type") + 
  xlab("Heterospecific Nursery predator (Y/N)") + 
  ylab("Nursery conspecific count") +
  geom_richtext(aes(x = 0.8, y =10), color = "black", 
                label = "*D. tinctorius*", size = 4)

#how about for actual density calculation
ggplot(subset(bw_choice, !(Predator_Y_N == "NA")),
       aes(x = Predator_Y_N, y = pool_dens_semiell, colour = Pool_Type))+  #y = pool_dens_cyl
  geom_jitter(size = 3, shape = 21, stroke = 1.5, alpha = 0.6,
              height = 0, width = 0.1) +
  stat_summary(fun.data = mean_cl_boot, #lets look at mean instead of median
               geom = "pointrange", # could also do crossbar, errorbar
               shape = 21,
               color = "black",
               fill = "white",
               size = 1, 
               stroke = 1.4) + 
  scale_fill_brewer(palette = "Spectral", 
                    name = "Pool type") + 
  xlab("Heterospecific Nursery predator (Y/N)") + 
  ylab("Nursery conspecific density") 


#not more predators in darker pools
ggplot(subset(bw_choice, !(Predator_Y_N == "NA")), 
              aes(x = Predator_Y_N, y = rMean_OG))+  #y = Swim
  geom_jitter(size = 3, shape = 21, stroke = 1.5, alpha = 0.6,
              height = 0.2, width = 0.1, aes(fill = Pool_Type)) +
  stat_summary(fun.data = mean_cl_boot, #lets look at mean instead of median
               geom = "pointrange", # could also do crossbar, errorbar
               shape = 21,
               color = "black",
               fill = "white",
               size = 1, 
               stroke = 1.4) + 
  scale_fill_brewer(palette = "Spectral", 
                    name = "Pool Type") + 
  xlab("Nursery predator (Y/N)") + 
  ylab("%R-channel reflectance")

#TURBIDITY IN EACH POOL
ggplot(activity, aes(y = rMean_OG, x = Pool_ID, group = Pool_ID)) + 
  geom_point(size = 3) + 
  gghighlight(rMean_OG < 100) + 
  #facet_wrap(~ Pool_ID) + 
  geom_hline(yintercept = 100, linetype = "dashed")+
  ylab("%R-channel reflectance") + 
  xlab("Pool ID")

```
